A Higher-Order Approach to Explicit Contexts in LF

### 2015-03-08 paper/paper.tex
Lmao, too many Ks.

%% Krary Stuff
\DeclareMathOperator\isvarop{\mathsf{isvar}}
\DeclareMathOperator\boundedop{\mathsf{bounded}}
\DeclareMathOperator\orderedop{\mathsf{ordered}}
\DeclareMathOperator\precedesop{\mathsf{precedes}}

@@

  Another technique advanced by Krary is to represent contexts explicitly, and
  then define a sequent judgement over them; this can be used to resolve the
  problem described above (and several others), but it comes at the cost of
  verbosity, and introduces difficulties when used to encode \emph{telescopes}
  in the LF, which are contexts where where each successive term has the
  previous bound variables free in it.  In this paper, I demonstrate a
  higher-order encoding of telescopes which can be used to faithfully encode
  the functional sequent judgement for MLTT~1979.

@@

Following Martin-L\"of, we give an extensional equality for all types (i.e.\
two types are equal when they have the same membership and equivalence
relations); we could choose an intensional/structural equality for types, but
for our purposes here, it is not necessary.

@@

\section{Explicit Contexts \`a la Krary}
In order to factor out functionality constraints, it will be necessary to
consider the use of contexts in the encoding, and then recast the judgements
above as being sequents, i.e.\ judgements with respect to a context. Krary's
first-order encoding of explicit contexts in the LF is essentially the
following:

>>>>

%% Crary Stuff
\DeclareMathOperator\isvarop{\mathsf{isvar}}
\DeclareMathOperator\boundedop{\mathsf{bounded}}
\DeclareMathOperator\orderedop{\mathsf{ordered}}
\DeclareMathOperator\precedesop{\mathsf{precedes}}

@@

  Another technique advanced by Crary is to represent contexts explicitly, and
  then define a sequent judgement over them; this can be used to resolve the
  problem described above (and several others), but it comes at the cost of
  verbosity, and introduces difficulties when used to encode \emph{telescopes}
  in the LF, which are contexts where where each successive term has the
  previous bound variables free in it.  In this paper, I demonstrate a
  higher-order encoding of telescopes which can be used to faithfully encode
  the functional sequent judgement for MLTT~1979.

@@

Following Martin-L\"of, we give an extensional equality for all types (i.e.\
two types are equal when they have the same membership and equivalence
relations); we could choose an intensional/structural equality for types, but
this question is orthogonal to the technique being demonstrated.

@@

\section{Explicit Contexts \`a la Crary}
In order to factor out functionality constraints, it will be necessary to
consider the use of contexts in the encoding, and then recast the judgements
above as being sequents, i.e.\ judgements with respect to a context. Crary's
first-order encoding of explicit contexts in the LF is essentially the
following:
